Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/intro.tex
put question generation into methodology; restructuring intro to the new outline (not done yet)

Wearable technologies, or ``wearables,'' are intimately related with both fields of ubiquitous computing and wearable computers. This \$700 million industry \cite{cmo} of electronically enhanced clothing items and accessories aims to interweave technological interaction into everyday life. A top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}. With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are transforming ubiquitous computing into a part of every day life. Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''

The constantly captured data from these devices has many benefits, ranging from a more natural, human-centered interface experience to a healthier, fitness-data inspired lifestyle. It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits over traditional devices.

@@

To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}. These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.

>>>>

Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} consisting of electronically enhanced clothing items and accessories aims to interweave technological interaction into everyday life. A top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}. With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are transforming ubiquitous computing into a part of every day life. Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''

The constantly captured data from these devices has many benefits, ranging from a more natural, human-centered interface experience to a healthier, fitness-data inspired lifestyle. There will likely be many more applications in the future which take advantage of such data. It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits over traditional devices.

@@

### 2015-03-04 tex-inputs/methodology.tex
put question generation into methodology; restructuring intro to the new outline (not done yet)

\section{Methodology}

>>>>

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}. These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.
